\mytitle

### 2012-03-26 papers/SAS2012/implicitization.tex
derniers résultats sur les domaines abstraits

Experimental results of our tool on the benchmark presented in
Fig~\ref{fig:projects} are given below. The precision of different
techniques is given in Table~\ref{tab:techniques}. The precision of
abstract domains and widening operators in given in
Table~\ref{tab:domain}.

@@

\label{sec:compare_domains}
\begin{sidewaystable}
\begin{center}
\setlength{\tabcolsep}{0.75ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{PK/GRID}}
& \multicolumn{3}{c|}{\textbf{POLY/POLY*}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK and
POLY),
Octagons (OCT), intervals (BOX), linear equalities (PKEQ) and linear congruences
(GRID). The last column compares the domain of Convex Polyhedra with the
improved widening operator from \cite{BagnaraHRZ05SCP} (POLY*), and Convex Polyhedra
using the classical widening operator (POLY). POLY and POLY* use the Parma
Polyhedral Library \cite{PPL}.
$\subsetneq$, $\supsetneq$ and ``unc.'' are defined as in Fig.~\ref{fig:techniques}.}
\label{tab:domain}
\end{sidewaystable}

>>>>

Experimental results of our tool on the benchmark presented in
Fig~\ref{fig:projects} are given below. The precision of different
techniques is given in Table~\ref{tab:techniques}. The precision of
abstract domains and widening operators is given in
Table~\ref{tab:domain}.

@@

\label{sec:compare_domains}
\begin{sidewaystable}
\begin{center}
\setlength{\tabcolsep}{0.75ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{PK/GRID}}
& \multicolumn{3}{c|}{\textbf{POLY/POLY*}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK and
POLY),
Octagons (OCT), intervals (BOX), linear equalities (PKEQ) and linear
inequalities with linear congruences
(GRID). The last column compares the domain of Convex Polyhedra with the
improved widening operator from \cite{BagnaraHRZ05SCP} (POLY*), and Convex Polyhedra
using the classical widening operator (POLY). POLY and POLY* use the Parma
Polyhedral Library \cite{PPL}.
$\subsetneq$, $\supsetneq$ and ``unc.'' are defined as in Fig.~\ref{fig:techniques}.}
\label{tab:domain}
\end{sidewaystable}
